Multisensor Architecture for an Intersection Management System

### 2018-03-02 ch3-arch_sys.tex
Added figures for processing blocks section

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"}. Or channel \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{"leg\_3"}.

@@

\subsubsection{Preprocessing}
\subsubsection{Feature Analysis}
\subsubsection{Pattern Recognition}
\subsubsection{Situation Assesment}
\subsubsection{Tools and Utilities}

>>>>

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.

@@

\subsubsection{Preprocessing}
\begin{description}
\item[laser\_background\_remove]laser\_bg\_remove
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/laser_bg_remove.pdf}
\caption{laser\_bg\_remove}
\label{laser_bg_remove}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/polar2cart.pdf}
\caption{polar\_to\_cartesian}
\label{polar_to_cartesian}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/laser_cart_merge.pdf}
\caption{laser\_cart\_merge}
\label{laser_cart_merge}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/points_to_clusters.pdf}
\caption{points\_to\_clusters}
\label{points_to_clusters}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/points_to_grid.pdf}
\caption{points\_to\_grid}
\label{points_to_grid}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/grid_to_occupancy_level.pdf}
\caption{grid\_to\_occupancy\_level}
\label{grid_to_occupancy_level}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/clusters_to_occupancy_level.pdf}
\caption{clusters\_to\_occupancy\_level}
\label{clusters_to_occupancy_level}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/occupancy_level_merge.pdf}
\caption{occupancy\_level\_merge}
\label{occupancy_level_merge}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/3/occupancy_level2int_state.pdf}
\caption{occupancy\_level\_to\_intersection\_state}
\label{occupancy_level2int_state}
\end{figure}

\end{description}

%{laser_background_remove}
\subsubsection{Feature Analysis}
\subsubsection{Pattern Recognition}
\subsubsection{Situation Assesment}
\subsubsection{Tools and Utilities}
